JavaScript is the programming language of HTML and web :\href{https://www.w3schools.com/js/}{w3schools}.\\
User rating of JS is $67.8\%$. See? how many people use JS. For become a great software developer or web developer, you must learn \textbf{JavaScript}. It seems impossible to be a developer without using JS. JavaScript provides an easy way to create interactive web pages smoothly.\\
All the functionality of JS in html written between $<$script$>$\dots$</$script$>$ tag.
\section{Why We Should Learn JS}
JavaScript is one of the 3 languages all web developer must learn.\\
\begin{enumerate}
 \item HTML
 \item CSS
 \item JavaScript(JS)
\end{enumerate}
Web pages are not the only place where \textbf{JS} is used. Many desktop and server programs use \textbf{JS}.
\section{Variable}
For declaring variable, use \textbf{\textcolor{red}{var}} keyword before variable name.\\
Syntax: \textcolor{red}{var variable\_name = value;}\\
If value is a string, write string value in single or double quotes. It's variable naming is same as C or C++. JavaScript is case sensitive. That's mean, var lastname and Lastname is not same.
\section{String}
JavaScript accepts both double and single quotes for assigning string values to variable.\\
var string;\\
string = "Kiron";\\
String operation as:\\
"Iqbal" + " " + "Kiron" is same as "Iqbal Kiron".
\section{Comments}
JS comment is fully same as C and C++ comments. JS supports both Oneline and Multiline comment.\\
Oneline comment: // or ///This is a comment.\\
Multiline comment: /*\dots*/